Title

### 2018-08-29 thesis/paper/paper.tex
Corrected wedges at line end

\section{Task}
Each property constraint will be modelled and evaluated as one set of rules per property per constraint, meaning each violating statement will be of a form similar to
\begin{equation}
\begin{split}
\text{violation}(X, Y, \text{propertyConstant}, Z) \leftarrow \text{atoms determining the violation}
\end{split}
\end{equation}
where propertyConstant denotes the constrained property. While it would be possible to load all data at once and restrict the property constant with a separate predicate akin to
\begin{equation}
\begin{split}
\text{violation}&(X, Y, \text{PROPERTY}, Z) \leftarrow \\
&\text{constrained}(\text{PROPERTY}, \text{constrainedConstant}) \wedge\\
&\text{rules determining the violation}
\end{split}
\end{equation}
this would increase the amount of facts loaded significantly while almost not reducing preprocessing.\\

@@

\subsection{Distinct values (Q21502410)}
The distinct values constraints requires two distinct constrained statements with the same value. 
While finding constrained statements with the same value is straightforward, violations only occur if the statements are actually different, i.e. have an unequal statement id.
\begin{equation*}
\begin{split}
\text{violation\_triple}&(S, I, \text{propertyConstant}, V) \leftarrow \\
&\text{statementEDB}(S, I, \text{propertyConstant}, V) \wedge \\
&\text{statementEDB}(O, X, \text{propertyConstant}, V) \wedge \\
&\text{unequal}(S, O)
\end{split}
\end{equation*}
While it is possible to set this constraint on qualifiers or references, this is currently not done and is thus not evaluated here.

@@

Violation are thus
\begin{equation*}
\begin{split}
\text{violation\_triple}&(S, I \text{propertyConstant}, V) \leftarrow \\
&\text{statementEDB}(S, I, \text{propertyConstant}, V) \wedge \\
&\text{unit}(V, U) \wedge \text{unequal}(\{A\}, U)
\end{split}
\end{equation*}
\begin{equation*}
\begin{split}
\text{violation\_qualifier}&(S, I \text{propertyConstant}, V) \leftarrow \\
&\text{qualifierEDB}(S, \text{propertyConstant}, V) \wedge \\
&\text{unit}(V, U) \wedge \text{unequal}(\{A\}, U)
\end{split}
\end{equation*}
\begin{equation*}
\begin{split}
\text{violation\_reference}&(S, I \text{propertyConstant}, V) \leftarrow \\
&\text{referenceEDB}(S, H, \text{propertyConstant}, V) \wedge \\
&\text{unit}(V, U) \wedge \text{unequal}(\{A\}, U)
\end{split}
\end{equation*}

\subsection{Allowed qualifiers (Q21510851)}
The allowed qualifiers constraint is violated if a qualifier on a constrained statement exists that is different from all allowed qualifiers. During pre-processing all qualifiers on constrained statements will be extracted and the inequality of their properties and the allowed qualifiers established. We will use the notation for set inequality as introduced in section \ref{subsec_3_allowed_units}. With \(A\) the set of allowed qualifiers the rule is:
\begin{equation*}
\begin{split}
\text{violation\_triple}&(S, I, \text{propertyConstant}, V) \leftarrow \\
&\text{statementEDB}(S, I, \text{propertyConstant}, V) \wedge \\
&\text{qualifierEDB}(S, Q, O) \wedge \text{unequal}(\{A\}, Q)
\end{split}
\end{equation*}

@@

\subsection{One-of qualifier value (Q52712340)}
The one-of qualifier value constraint is violated if a constrained statement has a qualifier with a value unequal to all allowed values. Inequality needs to be pre-processed between all values of qualifiers on constrained statements. With the set of allowed Values \(A\) the rules are
\begin{equation*}
\begin{split}
\text{violation\_triple}&(S, I, \text{propertyConstant}, V) \leftarrow \\
&\text{statementEDB}(S, I, \text{propertyConstant}, V) \wedge \\
&\text{qualifierEDB}(S, \text{qualifierProperty}, O) \wedge \text{unequal}(\{A\}, O)
\end{split}
\end{equation*}

@@

\subsection{Item requires statement (Q21503247)}
The item requires statement constraint requires the pre-processing of all item statements. Additionally, inequality between all properties of item statements and the required property as well as between all values and the allowed values has to be established. It occurs in two varieties, depending on if allowed values have been specified or not. The required term \(t\) is the  required property. Without separators the conjunction is
\begin{equation*}
\begin{split}
c_1 = &\text{statementEDB}(Q, I, \text{propertyConstant}, X) \wedge \\
&\text{statementEDB}(S, I, P, V) \wedge \text{unequal}(\text{requiredPropertyConstant}, P)
\end{split}
\end{equation*} \(\)
If a set of allowed values \(A\) has been specified, a second set of require-rules have to be introduced with
\begin{equation*}
\begin{split}
c_2 = &\text{statementEDB}(Q, I, \text{propertyConstant}, X) \wedge \\
&\text{statementEDB}(S, I, \text{requiredPropertyConstant}, V) \wedge \text{unequal}(\{A\}, V)
\end{split}
\end{equation*}
Note that the first set of rules is still required, since the preceding statements do not need to have the required property. In both cases violations can be found with
\begin{equation*}
\begin{split}
\text{violation\_triple}&(S, I, \text{propertyConstant}, V) \leftarrow \\
&\text{statementEDB}(S, I, \text{propertyConstant}, V) \wedge \\
&\text{statementEDB}(O, I, P, X) \wedge \text{last}(O, I) \wedge \\
&\text{require}(O, \text{propertyConstant}, \text{requiredPropertyConstant})
\end{split}
\end{equation*}

\subsection{Value requires statement (Q21510864)}
The value requires statement constraint is syntactically very similar to the previous item requires statement constraint. Instead of requiring a statement on the item of a constrained statement it requires it on the value. The pre-processing changes to extracting all value statements along the constrained statements and ordering them. Inequality need to be computed between all properties and all values on value statements. The conjunctions change in the first triple and are:
\begin{equation*}
\begin{split}
c_1 = &\text{statementEDB}(Q, R, \text{propertyConstant}, I) \wedge \\
&\text{statementEDB}(S, I, P, V) \wedge \text{unequal}(\text{requiredPropertyConstant}, P)
\end{split}
\end{equation*} \(\)
\begin{equation*}
\begin{split}
c_2 = &\text{statementEDB}(Q, R, \text{propertyConstant}, I) \wedge \\
&\text{statementEDB}(S, I, \text{requiredPropertyConstant}, V) \wedge \text{unequal}(\{A\}, V)
\end{split}
\end{equation*}
The final violation rule would then be:
\begin{equation*}
\begin{split}
\text{violation\_triple}&(S, I, \text{propertyConstant}, V) \leftarrow \\
&\text{statementEDB}(S, I, \text{propertyConstant}, V) \wedge \\
&\text{statementEDB}(O, V, P, X) \wedge \text{last}(O, V) \wedge \\
&\text{require}(O, \text{propertyConstant}, \text{requiredPropertyConstant})
\end{split}
\end{equation*}

\subsection{Inverse (Q21510855)}
The inverse constraint is similar to the value requires statement constraint in requiring a statement on a constrained value with a specific property. However, instead of putting no constraint or a list of fixed values on the required statements value it set a relative requirement: the constrained item, meaning \(t = R\). The pre-processing and inequalities thus remain the same, but the conjunctions change to 
\begin{equation*}
\begin{split}
c_1 = &\text{statementEDB}(Q, R, \text{propertyConstant}, I) \wedge \\
&\text{statementEDB}(S, I, P, V) \wedge \\
&\text{unequal}(\text{inversePropertyConstant}, P)
\end{split}
\end{equation*}
\begin{equation*}
\begin{split}
c_2 = &\text{statementEDB}(Q, R, \text{propertyConstant}, I) \wedge \\
&\text{statementEDB}(S, I, \text{inversePropertyConstant}, V) \wedge \\
&\text{unequal}(R, V)
\end{split}
\end{equation*}

@@

\subsection{Multi-value (Q21510857)}
The multi-value constraint requires a limited count of constrained statements. Alternatively, it could be said that if the item requires a second statement, the constraint is violated. Pre-processing extracts all items statements and inequality between all item statement properties as usual and the conjunction is 
\begin{equation*}
\begin{split}
c = &\text{statementEDB}(Q, I, \text{propertyConstant}, X) \wedge \\
&\text{statementEDB}(S, I, P, V) \wedge \text{unequal}(\text{propertyConstant}, P)
\end{split}
\end{equation*}
The predicate require\_second\([2]\) is introduced with the same meaning as require except that it will be applied after a required property has been found:
\begin{equation*}
\begin{split}
\text{require\_second}&(S, \text{propertyConstant}, \text{propertyConstant}) \leftarrow \\
&\text{next}(R, S) \wedge \text{statementEDB}(R, I, \text{propertyConstant}, C) \wedge \\
&\text{next}(Q, R) \wedge \text{require}(Q, \text{propertyConstant}, \text{propertyConstant})  \wedge c
\end{split}
\end{equation*}
\begin{equation*}
\begin{split}
\text{require\_second}&(S, \text{propertyConstant}, \text{propertyConstant}) \leftarrow \text{next}(R, S) \wedge \\
&\text{require\_second}(R, \text{propertyConstant}, \text{propertyConstant}) \wedge c
\end{split}
\end{equation*}
A violations would be any last statement requiring a second constrained statement.\\

@@

\subsubsection{No separators}
If the separator set is empty, the violation simply occurs if there are two constrained statements on the same item. 
\begin{equation}\label{eq_no_separators_triple}
\begin{split}
\text{violation\_triple}&(S, I, \text{propertyConstant}, V) \leftarrow \\
&\text{statementEDB}(S, I, \text{propertyConstant}, V) \wedge \\
&\text{statementEDB}(O, I, \text{propertyConstant}, X) \wedge \\
&\text{unequal}(S, O)
\end{split}
\end{equation}
For qualifiers and reference there is no ID whose inequality could be checked. However, since the statement ID and the property of a possible conflict are always the same, inequality can be tested on the values.
\begin{equation*}
\begin{split}
\text{violation\_qualifier}&(S, \text{propertyConstant}, V) \leftarrow \\
&\text{qualifierEDB}(S, \text{propertyConstant}, V) \wedge \\
&\text{qualifierEDB}(S, \text{propertyConstant}, X) \wedge \\
&\text{unequal}(V, X)
\end{split}
\end{equation*}
\begin{equation*}
\begin{split}
\text{violation\_reference}&(S, \text{propertyConstant}, V) \leftarrow \\
&\text{referenceEDB}(S, H, \text{propertyConstant}, V) \wedge \\
&\text{referenceEDB}(S, J, \text{propertyConstant}, X) \wedge \\
&\text{unequal}(V, X)
\end{split}
\end{equation*}
\todo{Check if all reference-rules look exactly like the qualifier rules and cut them out if it is so.}

@@

With qualifier non-existence established the violation can be found. Two statements form a violation if they are distinct as per equation \ref{eq_no_separators_triple} and additionally fulfil the condition that all qualifiers are either equal or non-existent. \(\forall X \subset S, Y = S \setminus X\) the following rule has to be added. Note that \(\text{predicate}(\{X\})\) denotes one atom for each element \(x \in X\) as introduced in section \ref{subsec_3_allowed_units}. With the predicate does\_not\_have\([2]\) linking a statement ID to the separator it does not have via 
\begin{equation*}
\begin{split}
\text{does\_not\_have}(S, R) \leftarrow &\text{statementEDB}(S, I, \text{propertyConstant}, C) \wedge \\
&\text{last\_qualifier}(S, P, V) \wedge \text{require}(S, P, V, \text{propertyConstant}, R)
\end{split}
\end{equation*}
and the predicate has\_same[2] linking two statement IDs to the separator for which the values are the same via
\begin{equation*}
\begin{split}
\text{has\_same}(S, O, Q) \leftarrow &\text{statementEDB}(S, I, \text{propertyConstant}, C) \wedge \\
&\text{statementEDB}(O, I, \text{propertyConstant}, X) \wedge \\
&\text{qualifierEDB}(S, Q, V) \wedge \text{qualifierEDB}(O, Q, V)
\end{split}
\end{equation*}
 for brevity the rules are
\begin{equation*}
\begin{split}
\text{violation\_triple}&(S, I, \text{propertyConstant}, V) \leftarrow \\
&\text{statementEDB}(S, I, \text{propertyConstant}, V) \wedge \\
&\text{statementEDB}(O, I, \text{propertyConstant}, C) \wedge \\
&\text{unequal}(S, O) \wedge \\
&\text{has\_same}(S, O, \{X\}) \wedge \\
&\text{does\_not\_have}(S, \{Y\}) \wedge \\
&\text{does\_not\_have}(O, \{Y\})
\end{split}
\end{equation*}

\subsection{Mandatory qualifier (Q21510856)}
The mandatory qualifier constraint needs to determine qualifier non-existence on constrained statements to find violations, which is similar to section \ref{subsubsec_with_separators}. All constrained statements and their qualifiers have to be extracted and the order of the qualifiers pre-processed. Inequality must be established between all qualifier properties and the conjunction is 
\begin{equation*}
\begin{split}
c = &\text{statementEDB}(S, I, \text{propertyConstant}, C) \wedge \\
&\text{qualifierEDB}(S, P, V) \wedge \text{unequal}(P, \text{requiredPropertyConstant})
\end{split}
\end{equation*}
With the usual require-pattern for qualifiers and the does\_not\_have rule added for brevity the violations would be
\begin{equation*}
\begin{split}
\text{violation\_triple}&(S, I, \text{propertyConstant}, V) \leftarrow \\
&\text{statementEDB}(S, I, \text{propertyConstant}, V) \wedge \text{does\_not\_have}(S, \text{requiredPropertyConstant})
\end{split}
\end{equation*}

@@

\subsubsection{No separators}
If the separator set is empty, the violation simply occurs if there are two constrained statements on the same item with the preferred rank. Thus the equation \ref{eq_no_separators_triple} is expanded to
\begin{equation*}
\begin{split}
\text{violation\_triple}&(S, I, \text{propertyConstant}, V) \leftarrow \\
&\text{statementEDB}(S, I, \text{propertyConstant}, V) \wedge \\
&\text{rank}(S, \text{preferredRankConstant}) \wedge \\
&\text{statementEDB}(O, I, \text{propertyConstant}, X) \wedge \\
&\text{rank}(O, \text{preferredRankConstant}) \wedge \\
&\text{unequal}(S, O)
\end{split}
\end{equation*}

\subsubsection{With separators}
As in the case above, the qualifier non-existence and violation rules are very similar to single value. The only change is the addition of the rank requirements as shown below.
\begin{equation*}
\begin{split}
\text{violation\_triple}&(S, I, \text{propertyConstant}, V) \leftarrow \\
&\text{statementEDB}(S, I, \text{propertyConstant}, V) \wedge \\
&\text{rank}(S, \text{preferredRankConstant}) \wedge \\
&\text{statementEDB}(O, I, \text{propertyConstant}, W) \wedge \\
&\text{rank}(O, \text{preferredRankConstant}) \wedge \\
&\text{unequal}(S, O) \wedge \\
&\text{has\_same}(S, O, \{X\}) \wedge \\
&\text{does\_not\_have}(S, \{Y\}) \wedge \\
&\text{does\_not\_have}(O, \{Y\})
\end{split}
\end{equation*}

>>>>

\section{Task}
Each property constraint will be modelled and evaluated as one set of rules per property per constraint, meaning each violating statement will be of a form similar to
\begin{equation}
\begin{split}
\text{violation}(X, Y, \text{propertyConstant}, Z) \leftarrow \text{atoms determining the violation}
\end{split}
\end{equation}
where propertyConstant denotes the constrained property. While it would be possible to load all data at once and restrict the property constant with a separate predicate akin to
\begin{equation}
\begin{split}
\text{violation}&(X, Y, \text{PROPERTY}, Z) \leftarrow \\
&\text{constrained}(\text{PROPERTY}, \text{constrainedConstant}) \wedge{} \\
&\text{rules determining the violation}
\end{split}
\end{equation}
this would increase the amount of facts loaded significantly while almost not reducing preprocessing.\\

@@

\subsection{Distinct values (Q21502410)}
The distinct values constraints requires two distinct constrained statements with the same value. 
While finding constrained statements with the same value is straightforward, violations only occur if the statements are actually different, i.e. have an unequal statement id.
\begin{equation*}
\begin{split}
\text{violation\_triple}&(S, I, \text{propertyConstant}, V) \leftarrow \\
&\text{statementEDB}(S, I, \text{propertyConstant}, V) \wedge{} \\
&\text{statementEDB}(O, X, \text{propertyConstant}, V) \wedge{} \\
&\text{unequal}(S, O)
\end{split}
\end{equation*}
While it is possible to set this constraint on qualifiers or references, this is currently not done and is thus not evaluated here.

@@

Violation are thus
\begin{equation*}
\begin{split}
\text{violation\_triple}&(S, I \text{propertyConstant}, V) \leftarrow \\
&\text{statementEDB}(S, I, \text{propertyConstant}, V) \wedge{} \\
&\text{unit}(V, U) \wedge \text{unequal}(\{A\}, U)
\end{split}
\end{equation*}
\begin{equation*}
\begin{split}
\text{violation\_qualifier}&(S, I \text{propertyConstant}, V) \leftarrow \\
&\text{qualifierEDB}(S, \text{propertyConstant}, V) \wedge{} \\
&\text{unit}(V, U) \wedge \text{unequal}(\{A\}, U)
\end{split}
\end{equation*}
\begin{equation*}
\begin{split}
\text{violation\_reference}&(S, I \text{propertyConstant}, V) \leftarrow \\
&\text{referenceEDB}(S, H, \text{propertyConstant}, V) \wedge{} \\
&\text{unit}(V, U) \wedge \text{unequal}(\{A\}, U)
\end{split}
\end{equation*}

\subsection{Allowed qualifiers (Q21510851)}
The allowed qualifiers constraint is violated if a qualifier on a constrained statement exists that is different from all allowed qualifiers. During pre-processing all qualifiers on constrained statements will be extracted and the inequality of their properties and the allowed qualifiers established. We will use the notation for set inequality as introduced in section \ref{subsec_3_allowed_units}. With \(A\) the set of allowed qualifiers the rule is:
\begin{equation*}
\begin{split}
\text{violation\_triple}&(S, I, \text{propertyConstant}, V) \leftarrow \\
&\text{statementEDB}(S, I, \text{propertyConstant}, V) \wedge{} \\
&\text{qualifierEDB}(S, Q, O) \wedge \text{unequal}(\{A\}, Q)
\end{split}
\end{equation*}

@@

\subsection{One-of qualifier value (Q52712340)}
The one-of qualifier value constraint is violated if a constrained statement has a qualifier with a value unequal to all allowed values. Inequality needs to be pre-processed between all values of qualifiers on constrained statements. With the set of allowed Values \(A\) the rules are
\begin{equation*}
\begin{split}
\text{violation\_triple}&(S, I, \text{propertyConstant}, V) \leftarrow \\
&\text{statementEDB}(S, I, \text{propertyConstant}, V) \wedge{} \\
&\text{qualifierEDB}(S, \text{qualifierProperty}, O) \wedge \text{unequal}(\{A\}, O)
\end{split}
\end{equation*}

@@

\subsection{Item requires statement (Q21503247)}
The item requires statement constraint requires the pre-processing of all item statements. Additionally, inequality between all properties of item statements and the required property as well as between all values and the allowed values has to be established. It occurs in two varieties, depending on if allowed values have been specified or not. The required term \(t\) is the  required property. Without separators the conjunction is
\begin{equation*}
\begin{split}
c_1 = &\text{statementEDB}(Q, I, \text{propertyConstant}, X) \wedge{} \\
&\text{statementEDB}(S, I, P, V) \wedge \text{unequal}(\text{requiredPropertyConstant}, P)
\end{split}
\end{equation*} \(\)
If a set of allowed values \(A\) has been specified, a second set of require-rules have to be introduced with
\begin{equation*}
\begin{split}
c_2 = &\text{statementEDB}(Q, I, \text{propertyConstant}, X) \wedge{} \\
&\text{statementEDB}(S, I, \text{requiredPropertyConstant}, V) \wedge \text{unequal}(\{A\}, V)
\end{split}
\end{equation*}
Note that the first set of rules is still required, since the preceding statements do not need to have the required property. In both cases violations can be found with
\begin{equation*}
\begin{split}
\text{violation\_triple}&(S, I, \text{propertyConstant}, V) \leftarrow \\
&\text{statementEDB}(S, I, \text{propertyConstant}, V) \wedge{} \\
&\text{statementEDB}(O, I, P, X) \wedge \text{last}(O, I) \wedge{} \\
&\text{require}(O, \text{propertyConstant}, \text{requiredPropertyConstant})
\end{split}
\end{equation*}

\subsection{Value requires statement (Q21510864)}
The value requires statement constraint is syntactically very similar to the previous item requires statement constraint. Instead of requiring a statement on the item of a constrained statement it requires it on the value. The pre-processing changes to extracting all value statements along the constrained statements and ordering them. Inequality need to be computed between all properties and all values on value statements. The conjunctions change in the first triple and are:
\begin{equation*}
\begin{split}
c_1 = &\text{statementEDB}(Q, R, \text{propertyConstant}, I) \wedge{} \\
&\text{statementEDB}(S, I, P, V) \wedge \text{unequal}(\text{requiredPropertyConstant}, P)
\end{split}
\end{equation*} \(\)
\begin{equation*}
\begin{split}
c_2 = &\text{statementEDB}(Q, R, \text{propertyConstant}, I) \wedge{} \\
&\text{statementEDB}(S, I, \text{requiredPropertyConstant}, V) \wedge \text{unequal}(\{A\}, V)
\end{split}
\end{equation*}
The final violation rule would then be:
\begin{equation*}
\begin{split}
\text{violation\_triple}&(S, I, \text{propertyConstant}, V) \leftarrow \\
&\text{statementEDB}(S, I, \text{propertyConstant}, V) \wedge{} \\
&\text{statementEDB}(O, V, P, X) \wedge \text{last}(O, V) \wedge{} \\
&\text{require}(O, \text{propertyConstant}, \text{requiredPropertyConstant})
\end{split}
\end{equation*}

\subsection{Inverse (Q21510855)}
The inverse constraint is similar to the value requires statement constraint in requiring a statement on a constrained value with a specific property. However, instead of putting no constraint or a list of fixed values on the required statements value it set a relative requirement: the constrained item, meaning \(t = R\). The pre-processing and inequalities thus remain the same, but the conjunctions change to 
\begin{equation*}
\begin{split}
c_1 = &\text{statementEDB}(Q, R, \text{propertyConstant}, I) \wedge{} \\
&\text{statementEDB}(S, I, P, V) \wedge{} \\
&\text{unequal}(\text{inversePropertyConstant}, P)
\end{split}
\end{equation*}
\begin{equation*}
\begin{split}
c_2 = &\text{statementEDB}(Q, R, \text{propertyConstant}, I) \wedge{} \\
&\text{statementEDB}(S, I, \text{inversePropertyConstant}, V) \wedge{} \\
&\text{unequal}(R, V)
\end{split}
\end{equation*}

@@

\subsection{Multi-value (Q21510857)}
The multi-value constraint requires a limited count of constrained statements. Alternatively, it could be said that if the item requires a second statement, the constraint is violated. Pre-processing extracts all items statements and inequality between all item statement properties as usual and the conjunction is 
\begin{equation*}
\begin{split}
c = &\text{statementEDB}(Q, I, \text{propertyConstant}, X) \wedge{} \\
&\text{statementEDB}(S, I, P, V) \wedge \text{unequal}(\text{propertyConstant}, P)
\end{split}
\end{equation*}
The predicate require\_second\([2]\) is introduced with the same meaning as require except that it will be applied after a required property has been found:
\begin{equation*}
\begin{split}
\text{require\_second}&(S, \text{propertyConstant}, \text{propertyConstant}) \leftarrow \\
&\text{next}(R, S) \wedge \text{statementEDB}(R, I, \text{propertyConstant}, C) \wedge{} \\
&\text{next}(Q, R) \wedge \text{require}(Q, \text{propertyConstant}, \text{propertyConstant})  \wedge c
\end{split}
\end{equation*}
\begin{equation*}
\begin{split}
\text{require\_second}&(S, \text{propertyConstant}, \text{propertyConstant}) \leftarrow \text{next}(R, S) \wedge{} \\
&\text{require\_second}(R, \text{propertyConstant}, \text{propertyConstant}) \wedge c
\end{split}
\end{equation*}
A violations would be any last statement requiring a second constrained statement.\\

@@

\subsubsection{No separators}
If the separator set is empty, the violation simply occurs if there are two constrained statements on the same item. 
\begin{equation}\label{eq_no_separators_triple}
\begin{split}
\text{violation\_triple}&(S, I, \text{propertyConstant}, V) \leftarrow \\
&\text{statementEDB}(S, I, \text{propertyConstant}, V) \wedge{} \\
&\text{statementEDB}(O, I, \text{propertyConstant}, X) \wedge{} \\
&\text{unequal}(S, O)
\end{split}
\end{equation}
For qualifiers and reference there is no ID whose inequality could be checked. However, since the statement ID and the property of a possible conflict are always the same, inequality can be tested on the values.
\begin{equation*}
\begin{split}
\text{violation\_qualifier}&(S, \text{propertyConstant}, V) \leftarrow \\
&\text{qualifierEDB}(S, \text{propertyConstant}, V) \wedge{} \\
&\text{qualifierEDB}(S, \text{propertyConstant}, X) \wedge{} \\
&\text{unequal}(V, X)
\end{split}
\end{equation*}
\begin{equation*}
\begin{split}
\text{violation\_reference}&(S, \text{propertyConstant}, V) \leftarrow \\
&\text{referenceEDB}(S, H, \text{propertyConstant}, V) \wedge{} \\
&\text{referenceEDB}(S, J, \text{propertyConstant}, X) \wedge{} \\
&\text{unequal}(V, X)
\end{split}
\end{equation*}
\todo{Check if all reference-rules look exactly like the qualifier rules and cut them out if it is so.}

@@

With qualifier non-existence established the violation can be found. Two statements form a violation if they are distinct as per equation \ref{eq_no_separators_triple} and additionally fulfil the condition that all qualifiers are either equal or non-existent. \(\forall X \subset S, Y = S \setminus X\) the following rule has to be added. Note that \(\text{predicate}(\{X\})\) denotes one atom for each element \(x \in X\) as introduced in section \ref{subsec_3_allowed_units}. With the predicate does\_not\_have\([2]\) linking a statement ID to the separator it does not have via 
\begin{equation*}
\begin{split}
\text{does\_not\_have}(S, R) \leftarrow &\text{statementEDB}(S, I, \text{propertyConstant}, C) \wedge{} \\
&\text{last\_qualifier}(S, P, V) \wedge \text{require}(S, P, V, \text{propertyConstant}, R)
\end{split}
\end{equation*}
and the predicate has\_same[2] linking two statement IDs to the separator for which the values are the same via
\begin{equation*}
\begin{split}
\text{has\_same}(S, O, Q) \leftarrow &\text{statementEDB}(S, I, \text{propertyConstant}, C) \wedge{} \\
&\text{statementEDB}(O, I, \text{propertyConstant}, X) \wedge{} \\
&\text{qualifierEDB}(S, Q, V) \wedge \text{qualifierEDB}(O, Q, V)
\end{split}
\end{equation*}
 for brevity the rules are
\begin{equation*}
\begin{split}
\text{violation\_triple}&(S, I, \text{propertyConstant}, V) \leftarrow \\
&\text{statementEDB}(S, I, \text{propertyConstant}, V) \wedge{} \\
&\text{statementEDB}(O, I, \text{propertyConstant}, C) \wedge{} \\
&\text{unequal}(S, O) \wedge{} \\
&\text{has\_same}(S, O, \{X\}) \wedge{} \\
&\text{does\_not\_have}(S, \{Y\}) \wedge{} \\
&\text{does\_not\_have}(O, \{Y\})
\end{split}
\end{equation*}

\subsection{Mandatory qualifier (Q21510856)}
The mandatory qualifier constraint needs to determine qualifier non-existence on constrained statements to find violations, which is similar to section \ref{subsubsec_with_separators}. All constrained statements and their qualifiers have to be extracted and the order of the qualifiers pre-processed. Inequality must be established between all qualifier properties and the conjunction is 
\begin{equation*}
\begin{split}
c = &\text{statementEDB}(S, I, \text{propertyConstant}, C) \wedge{} \\
&\text{qualifierEDB}(S, P, V) \wedge \text{unequal}(P, \text{requiredPropertyConstant})
\end{split}
\end{equation*}
With the usual require-pattern for qualifiers and the does\_not\_have rule added for brevity the violations would be
\begin{equation*}
\begin{split}
\text{violation\_triple}&(S, I, \text{propertyConstant}, V) \leftarrow \\
&\text{statementEDB}(S, I, \text{propertyConstant}, V) \wedge \text{does\_not\_have}(S, \text{requiredPropertyConstant})
\end{split}
\end{equation*}

@@

\subsubsection{No separators}
If the separator set is empty, the violation simply occurs if there are two constrained statements on the same item with the preferred rank. Thus the equation \ref{eq_no_separators_triple} is expanded to
\begin{equation*}
\begin{split}
\text{violation\_triple}&(S, I, \text{propertyConstant}, V) \leftarrow \\
&\text{statementEDB}(S, I, \text{propertyConstant}, V) \wedge{} \\
&\text{rank}(S, \text{preferredRankConstant}) \wedge{} \\
&\text{statementEDB}(O, I, \text{propertyConstant}, X) \wedge{} \\
&\text{rank}(O, \text{preferredRankConstant}) \wedge{} \\
&\text{unequal}(S, O)
\end{split}
\end{equation*}

\subsubsection{With separators}
As in the case above, the qualifier non-existence and violation rules are very similar to single value. The only change is the addition of the rank requirements as shown below.
\begin{equation*}
\begin{split}
\text{violation\_triple}&(S, I, \text{propertyConstant}, V) \leftarrow \\
&\text{statementEDB}(S, I, \text{propertyConstant}, V) \wedge{} \\
&\text{rank}(S, \text{preferredRankConstant}) \wedge{} \\
&\text{statementEDB}(O, I, \text{propertyConstant}, W) \wedge{} \\
&\text{rank}(O, \text{preferredRankConstant}) \wedge{} \\
&\text{unequal}(S, O) \wedge{} \\
&\text{has\_same}(S, O, \{X\}) \wedge{} \\
&\text{does\_not\_have}(S, \{Y\}) \wedge{} \\
&\text{does\_not\_have}(O, \{Y\})
\end{split}
\end{equation*}
